---
title: "Custom estimand functions: means and contrasts"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{estimand-functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# Load the package

```{r setup}
library(precisionSim)
```

# Create a model

We'll use the sleepstudy data from the `lme4` package, and create a very simple model. In practice, this could be pilot data or from another (related) study.

```{r}
#get data
data_cake <- lme4::cake

#create model
model_cake <- lme4::lmer(angle ~ recipe + temp + (1 | recipe:replicate), data = data_cake)

```

# Marginal means

In the first instance, we demonstrate a function that estimates the marginal means and 95%CI using the `emmeans` package. 

The package expects a function that takes the lme4 model as an input, and produces a data.frame with columns for 'estimand', 'estimate', 'lower', and 'upper'. Here, we just do so for the beta coefficient for 'Task': 

```{r}
#marginal means function
recipe_means <- function(fitted_model) {
  
  marginal_means <- emmeans::emmeans(fitted_model, specs = ~ recipe)
  
  ci <- as.data.frame(stats::confint(marginal_means, level = 0.95))
  
  data.frame(
    estimand = paste("Adjusted mean for recipe", ci$recipe),
    estimate = ci$emmean,
    lower = ci$lower.CL,
    upper = ci$upper.CL
  )
}

```

We can quickly test this function as follows:

```{r}
recipe_means(model_cake)
```

## Run the simulations

As usual, we'll run 100 simulations for simplicity and efficiency, but for the real thing, do more (e.g., 5000).

```{r}
#run precision simulation
sim1 <- precisionSim(
  fit = model_cake,
  interval_fun = recipe_means,
  target_width = c(5, 7, 9),
  nsim = 100,
  seed = 123
)

#summary
summary(sim1)
```

## Visualise

We can visualise our results in two ways: 1) "assurance" which should a ecdf, and 2) "distribution" which shows a histogram of the simulated widths. 

```{r}
#visualise
plot(sim1, type="assurance")
```

## Determine width at pre-specified assurance 

We can also take our results, and determine with confidence interval width at a pre-specified assurance probability. 

```{r}
#determine widths at 50%, 75% and 90% assurance levels
quantile(sim1, prob = c(0.5, 0.75, 0.9))
```

# Pairwise contrast

Now we'll demonstrate pairwise contrasts, again using the `emmeans` package.

```{r}
#pairwise contrast function
recipe_pairwise <- function(fitted_model) {
  
  comparisons <- emmeans::emmeans(fitted_model, pairwise ~ recipe,adjust = "none")
  
  ci <- as.data.frame(stats::confint(comparisons$contrasts,level = 0.95,adjust = "none"))
  
  data.frame(
    estimand = ci$contrast,
    estimate = ci$estimate,
    lower = ci$lower.CL,
    upper = ci$upper.CL
  )
}

#test
recipe_pairwise(model_cake)
```

## Run the simulations

```{r}
#run precision simulation
sim2 <- precisionSim(
  fit = model_cake,
  interval_fun = recipe_pairwise,
  target_width = c(7, 9, 11),
  nsim = 100,
  seed = 123
)

#summary
summary(sim2)
```

## Visualise

```{r}
#plot
plot(sim2)
```

## Determine width at pre-specified assurance 

```{r}
#check different assurance probabilities
quantile(sim2, prob = c(0.50, 0.80, 0.95))
```

# Adjusting for covariates

In some instances, we may want our estimands to adjust for a covariate. Here is an example function for an adjusted marginal mean.

```{r}
recipe_means_at_200 <- function(fitted_model) {

  marginal_means <- emmeans::emmeans(fitted_model,specs = ~ recipe,at = list(temp = 200 ))

  ci <- as.data.frame(stats::confint(marginal_means,level = 0.95))

  data.frame(
    estimand = paste("Recipe", ci$recipe, "mean at 200"),
    estimate = ci$emmean,
    lower = ci$lower.CL,
    upper = ci$upper.CL
  )
}

#test
recipe_means_at_200(model_cake)
```

The same could be done for pairwise contrasts or interaction models.
