---
title: "Simulate confidence interval widths at multiple sample sizes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{simulate-sample-sizes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Load the package

```{r setup}
library(precisionSim)
```

# Create a model

We'll again use the sleepstudy data from the `lme4` package, and create a very simple model. In practice, this could be pilot data or from another (related) study.

```{r}
#get data
data_sleep <- lme4::sleepstudy

#create model
mod1 <- lme4::lmer(Reaction ~ Days + (1|Subject), data = data_sleep)

```

# Create the extended model

We can use the `simr::extend()` to increase the sample size of our model to n=50:

```{r}
mod_extended <- simr::extend(mod1, along = "Subject", n = 40)
```

# Create the interval function

We then need to create a custom function that take the lme4 model as an input, and produces a data.frame with columns for 'estimand', 'estimate', 'lower', and 'upper'. Here, we just do so for the beta coefficient for 'Task': 

```{r}
#define function to get interval of interest
interval_function <- function(fitted_model){

  ci <- suppressMessages(confint(fitted_model))

  return(
    data.frame(
      estimand = "Days",
      estimate = lme4::fixef(fitted_model)[[2]],
      lower = ci[4,1],
      upper = ci[4,2]
    )
  )

}
```

We can quickly test this function as follows:

```{r}
interval_function(mod1)
```

Note that in this instance we only have  one estimand, but multiple estimands can be produced by adding more rows to our outputs data frame. 

# Run the simulations

We'd normally run more than 100 simulations (e.g., 5000), but for simplicity and efficiency we just run 100 

```{r}
#run 100 simulations for ease (should be higher for the real thing e.g., 5000)
sim1 <- precisionCurve(mod_extended,
                     target_width = c(3,4,5), #different widths to test
                     interval_fun = interval_function, #our custom function
                     along = "Subject", #variable were are simulating along
                     breaks = c(20, 30, 40), #number of levels of 'Subject' to simulate
                     prob = 0.80, #assurance probability
                     mc_conf_level = 0.95, #monte carlo confidence level for our probability 
                     nsim = 100, #number of simulations, usually go higher (e.g., 5000)
                     seed = 123) #seed

#summary
summary(sim1)
```

You can see that once we hit n=30, our lowest confidence interval width of 3 was achieved 100% of the time.

# Visualise

We can visualise our results in two ways: 1) "curve" which plot the assurance probability (with its 95% monte carlo confidence intervals) at each sample size, 2) "assurance" which should a ecdf, and 3) "distribution" which shows a histogram of the simulated widths. 

```{r}
#visualise
plot(sim1, type="curve")
plot(sim1, type="assurance")
plot(sim1, type="distribution")
```

# Determine width at pre-specified assurance 

We can also take our results, and determine with confidence interval width at a pre-specified assurance probability for each simulated sample size. 

```{r}
#determine widths at 50%, 75% and 90% assurance levels
quantile(sim1, prob = c(0.5, 0.75, 0.9))
```

# Re-run assurance tests

In some instances, we may want to re-run the assurance test with different parameters (e.g., assurance probabilities of target widths), but we don't necessarily need to re-run the computationally demanding simulations. In this instance, we can use the `assurance_test()` function.

```{r}
sim1_r <- assurance_test(sim1, target_width = c(2.5, 3.5))
```

This returns an object of the same structure as the original input object (i.e., `precisionCurve` or `precisionSim`). 

```{r}
#summary
summary(sim1_r)

#visualise
plot(sim1_r)
```
